Completing correlation matrices

### 2021-11-24 paper/paper_risk.tex
Small changes. Submitted to Risk.

\section{Introduction}
Modern financial models are driven by a large number of stochastic variables. These stochastic variables are usually correlated which creates the need to determine the coefficients of the underlying correlation matrix. Since the number of correlation coefficients increases quadratically with the number of stochastic variables, this number can become very large. While it would be desirable to calibrate all these coefficients this is in practice not possible because such a calibration procedure would be too slow, too unstable, or would require calibration instruments for which quotes can not be obtained. The issue of stability is especially important in a risk neutral setup where daily calibrations might display undesired fluctuations if the calibration is not stable. Hybrid models are another source of undetermined correlation coefficients. Two calibrated models might be parts of a larger model. While the coefficients for the individual models have been determined in separate calibrations, the coefficients that mix variables from the two different models are undetermined. In a large model, with many smaller constituent models, the number of such coefficients can constitute the bulk of the matrix.

>>>>

\section{Introduction}
Modern financial models are driven by a large number of stochastic variables. These normally distributed stochastic variables are usually correlated which creates the need to determine the coefficients of the underlying correlation matrix. Since the number of correlation coefficients increases quadratically with the number of stochastic variables, this number can become very large. While it would be desirable to calibrate all these coefficients this is in practice not possible because such a calibration procedure would be too slow, too unstable, or would require calibration instruments for which quotes can not be obtained. The issue of stability is especially important in a risk neutral setup where daily calibrations might display undesired fluctuations if the calibration is not stable. Hybrid models are another source of undetermined correlation coefficients. Two calibrated models might be parts of a larger model. While the coefficients for the individual models have been determined in separate calibrations, the coefficients that mix variables from the two different models are undetermined. In a large model, with many smaller constituent models, the number of such coefficients can constitute the bulk of the matrix.
